### 2025-01-10 ECE159 Lecture Notes/main.tex
Add Force-Separation Curve and update lecture notes

\subsection{Resistance}
\paragraph{Ohm's Law} Ohm's Law states that the current through a resistor is proportional to the voltage across it.
\begin{equation}
    V = IR
\end{equation}
\paragraph{Resistivity} The resistance of a material is proportional to the length of the material and inversely proportional to the cross-sectional area of the material.
\begin{equation}
    R = \rho \frac{l}{A}
\end{equation}
\paragraph{Short and Open Circuits} A short circuit is a circuit with no resistance, while an open circuit is a circuit with infinite resistance.
\paragraph{Conductance} The reciprocal of resistance is conductance. The unit of conductance is mho (ohm spelled backwards), \rotatebox[origin=c]{180}{$\Omega$}.
\begin{equation}
    G = \frac{1}{R}
\end{equation}
\paragraph{Power in Resistors} The power dissipated in a resistor is given by:
\begin{equation}
    P = I^2R = \frac{V^2}{R}
\end{equation}

\section{DC Circuits}
\paragraph{}

>>>>

\subsection{Resistance}
\paragraph{Ohm's Law} Ohm's Law states that the current through a resistor is proportional to the voltage across it.
\begin{equation}
    V = IR
\end{equation}
\paragraph{Resistivity} The resistance of a material is proportional to the length of the material and inversely proportional to the cross-sectional area of the material.
\begin{equation}
    R = \rho \frac{l}{A}
\end{equation}
\paragraph{Short and Open Circuits} A short circuit is a circuit with no resistance, while an open circuit is a circuit with infinite resistance.
\paragraph{Conductance} The reciprocal of resistance is conductance. The unit of conductance is mho (ohm spelled backwards), \rotatebox[origin=c]{180}{$\Omega$}.
\begin{equation}
    G = \frac{1}{R}
\end{equation}
\paragraph{Power in Resistors} The power dissipated in a resistor is given by:
\begin{equation}
    P = I^2R = \frac{V^2}{R}
\end{equation}
\paragraph{Resistors in Series} If resistors are placed in series with each other, their current must be the same, The equivalent resistance of resistors in series is the sum of the resistances.
\begin{equation}
    R_{\text{eq}} = R_1 + R_2 + \dots + R_n
\end{equation}
\paragraph{Resistors in Parallel} If resistors are placed in parallel with each other, their voltage must be the same. The equivalent resistance of resistors in parallel is the reciprocal of the sum of the reciprocals of the resistances.
\begin{equation}
    \frac{1}{R_{\text{eq}}} = \frac{1}{R_1} + \frac{1}{R_2} + \dots + \frac{1}{R_n}
\end{equation}
\paragraph{Comination of Series and Parallel Resistors} To find the equivalent resistance of a combination of series and parallel resistors, first find the equivalent resistance of the resistors in series, then find the equivalent resistance of the resistors in parallel.
\subsection{Node, Branch, and Loop}
\paragraph{} Three important ideas in electric circuit analysis are:
\begin{enumerate}
    \item \textbf{Branch}: A branch is an element in an electric circuit, such as a source or a resistor.
    \item \textbf{Node}: A point of connection of two or more branches within an electric circuit.
    \item \textbf{Loop}: Any closed path in an electric circuit. To form a loop, one must start and end at the same point and never pass through the same node twice.
\end{enumerate}
\section{DC Circuits}
\paragraph{}

### 2025-01-10 ESC195 Lecture Notes/main.tex
Add Force-Separation Curve and update lecture notes

\end{example}
\paragraph{} 
\end{document}

>>>>

\subsection{Trigonometric Integrals}
\paragraph{Case I} This is the case I trigonometric integrals, the strategy is using the pythagorean identity.
\paragraph{} We want to solve the class of integrals:
\begin{equation}
 \int \sin^n(x) \cos^m(x) \, dx
\end{equation}
, where $m$ or $n$ is odd.
\begin{example}
We want to solve the integral:
$$ I = \int \sin^3(x) \cos^2(x) dx $$
We use the identity: $ \sin^2(x) = 1 - \cos^2(x)$. Thus, the integral becomes:
\begin{align*}
    I &= \int \sin(x)(1 - \cos^2(x)) \cos^2(x) \, dx \\
    &= \int (\cos^2(x) \sin(x) - \cos^4(x) \sin(x)) \, dx
\end{align*} 
which is now easily solvable with substution $u=\cos(x)$.
\paragraph{Case II} The follwoing is generally solvable via case I and case III below. In general, we solve the integral by reducing the power of the trigonometric functions to arrive at a solvable integral Case I or III.
\paragraph{} We want to solve the class of integrals:
\begin{equation} \int \sin^n(x) \cos^m(x) \, dx \end{equation}
, where $m$ and $n$ is even.
\begin{example}
We want to solve the integral:
$$ I = \int \sin^2(x) \cos^4(x) \, dx $$
We can apply the double angle formulas:
\begin{align}
    \sin(x)\cos(x) &= \frac{1}{2} \sin(2x) \\
    \sin^2(x) &= \frac{1 - \cos(2x)}{2} \\
    \cos^2(x) &= \frac{1 + \cos(2x)}{2}
\end{align}
Thus, the integral becomes:
$$ I = \frac{1}{8} \int \sin^2(2x) \, dx + \frac{1}{8} \int \cos(2x)\sin^2(2x) \, dx $$
\paragraph{Case III} This is the case III trigonometric integrals, the strategy is using the reduction formula via IBP.
\paragraph{Reduction Formula} We can solve integrals by reducing the power of the trigonometric functions. These are done using IBP and trigonometric identities.
\paragraph{} We want to solve the classes of integrals:
\begin{equation} 
    \int \sin^n(x) \, dx, \quad \int \cos^n(x) \, dx 
\end{equation}
, where $n$ is a positive integer. For demonstartion, We can obtain the reduction formula of $\sin^n(x)$ via IBP.
\begin{align*}
    I_n &= \int \sin^n(x) \, dx \\
    &= \int \sin^{n-1}(x) \sin(x) \, dx \\
    &= \frac{-\cos(x) \sin^{n-1}(x)}{n} + \frac{(n-1)}{n} \int \cos^2(x) \sin^{n-2}(x) \, dx \\
    &= \frac{-\cos(x) \sin^{n-1}(x)}{n} + \frac{(n-1)}{n} I_{n-2}
\end{align*}
\paragraph{Case IV} The following is generally solvable via simple trigonometric integrals. In general, we solve the integral by applying the angle sum formulas.
\paragraph{} We want to solve the classes of integrals:
\begin{equation}
    \int \sin(mx) \cos(nx) \, dx, \quad \int \sin(mx) \sin(nx) \, dx, \quad \int \cos(mx) \cos(nx) \, dx 
\end{equation}
We could apply the angle sum formulas:
\begin{align}
    \sin(mx)\cos(nx) &= \frac{1}{2} \left[ \sin((m+n)x) + \sin((m-n)x) \right] \\
    \sin(mx)\sin(nx) &= \frac{1}{2} \left[ \cos((m-n)x) - \cos((m+n)x) \right] \\
    \cos(mx)\cos(nx) &= \frac{1}{2} \left[ \cos((m-n)x) + \cos((m+n)x) \right]
\end{align}
\paragraph{Case V} The following is generally solvable via the following trigonometric identities listed below, which convert it into a reduction formula.
\begin{align}
    \tan^2(x) &= \sec^2(x) - 1 \label{eq:tan2} \\
    \cot^2(x) &= \csc^2(x) - 1 \label{eq:cot2}  \\
    \frac{d}{dx} \tan(x) &= \sec^2(x)
\end{align}
\paragraph{} We want to solve the classes of integral:
\begin{equation}
    \int \tan^n(x) \, dx, \quad \int \cot^n(x) \, dx 
\end{equation}
We know that $tan^2(x) = \sec^2(x) - 1$. Thus, we can solve the integral by reducing the power of the tangent function.
\paragraph{Case VI} The following is generally solvable via the trigonometric identities (\ref{eq:tan2}) and (\ref{eq:cot2}).
\paragraph{} We want to solve the classes of integral:
\begin{equation} 
    \int \tan^m(x) \sec^n(x) \, dx, \quad \int \cot^m(x) \csc^n(x) \, dx 
\end{equation}
We can solve the integral by reducing the power of the converted trigonometric functions using (\ref{eq:tan2}) and (\ref{eq:cot2}).
\paragraph{Case VII} The following is generally solvable via the trigonometric identities (\ref{eq:tan2}) and (\ref{eq:cot2}).
\paragraph{} We want to solve the classes of integral:
\begin{equation} \int \tan^m(x) \sec^n(x) \, dx, \quad \int \cot^m(x) \csc^n(x) \, dx \end{equation}
We can solve the integral by converting between the tangent and secant functions using the trigonometric identities.
\paragraph{Case VIII} This is the case VIII integrals, the strategy is using the trigonometric substitution.
\paragraph{Trigonometric Substitution} We can solve integrals by substituting the trigonometric functions with other trigonometric functions.
\begin{example}
We want to solve the integral:
$$ \int \frac{dx}{\sqrt{1 - x^2}} $$
We can substitute $x = \sin(\theta)$, then $dx = \cos(\theta) \, d\theta$. The integral becomes:
$$ \int \frac{\cos(\theta) \, d\theta}{\sqrt{1 - \sin^2(\theta)}} = \int \frac{\cos(\theta) \, d\theta}{\cos(\theta)} = \int d\theta = \theta + C. $$
\paragraph{} In general, we can use the following substitutions:
\begin{itemize}
    \item $x = a\sin(\theta)$ for $\sqrt{a^2 - x^2}$,
    \item $x = a\tan(\theta)$ for $\sqrt{a^2 + x^2}$,
    \item $x = a\sec(\theta)$ for $\sqrt{x^2 - a^2}$.
\end{itemize}
\paragraph{Summary} We can solve trigonometric integrals by using the following strategies:
\begin{table}[h!]
    \centering
    \begin{tabular}{|c|l|}
    \hline
    \textbf{Case} & \textbf{Strategy and General Form} \\ \hline
    I   & Use \(\sin^2(x) + \cos^2(x) = 1\); simplify using substitution. \\
        & General Form: \(\int \sin^n(x) \cos^m(x) dx\), where \(m\) or \(n\) is odd. \\ \hline
    II  & Convert to Case I and Case III using double angle formulas. \\
        & General Form: \(\int \sin^n(x) \cos^m(x) dx\), where both \(m\) and \(n\) are even. \\ \hline
    III & Apply reduction formulas derived via integration by parts. \\
        & General Form: \(\int \sin^n(x) dx\) or \(\int \cos^n(x) dx\). \\ \hline
    IV  & Use angle sum formulas to simplify. \\
        & General Form: \(\int \sin(mx) \cos(nx) dx\). \\ \hline
    V   & Reduce tangent/cotangent powers using \(\tan^2(x) = \sec^2(x) - 1\) and substitution. \\
        & General Form: \(\int \tan^n(x) dx\) or \(\int \cot^n(x) dx\). \\ \hline
    VI  & Convert to Case V via Pythagorean identities. \\
        & General Form: \(\int \tan^m(x) \sec^n(x) dx\) or \(\int \cot^m(x) \csc^n(x) dx\). \\ \hline
    VII & Convert between tangent and secant functions for simplification. \\
        & General Form: \(\int \tan^m(x) \sec^n(x) dx\). \\ \hline
    VIII & Use trigonometric substitution: \(x = a \sin(\theta), a \tan(\theta), a \sec(\theta)\). \\
         & General Form: \(\int \frac{dx}{\sqrt{a^2 - x^2}}, \int \frac{dx}{\sqrt{a^2 + x^2}}, \int \frac{dx}{\sqrt{x^2 - a^2}}\). \\ \hline
    \end{tabular}
    \caption{Strategies and General Forms for Case I-VIII Integrals}
\end{table}

\section{Hyperbolic Trigonometric Functions}
\begin{definition}[Hyperbolic Sine]
    The hyperbolic sine function is defined as:
    \begin{equation} \sinh(x) = \frac{e^x - e^{-x}}{2}. \end{equation}
\end{definition}
\begin{definition}[Hyperbolic Cosine]
    The hyperbolic cosine function is defined as:
    \begin{equation}  \cosh(x) = \frac{e^x + e^{-x}}{2}. \end{equation}
\end{definition}
\paragraph{Properties} These combinations of exponential functions have properties similar to the trigonometric functions.
\paragraph{Derivatives} The derivatives of the hyperbolic functions are:
\begin{align}
    \frac{d}{dx} \sinh(x) &= \cosh(x), \\
    \frac{d}{dx} \cosh(x) &= \sinh(x).
\end{align}
\paragraph{Identities} The hyperbolic functions satisfy the following identities:
\begin{align}
    \cosh^2(x) - \sinh^2(x) &= 1, \\
    \cosh(2x) &= \cosh^2(x) + \sinh^2(x), \\
    \sinh(2x) &= 2\sinh(x)\cosh(x).
\end{align}
\paragraph{Hyperbola} The hyperbolic functions are related to the hyperbola $x^2 - y^2 = 1$. Simiar to the circle, the hyperbola can be parametrized by the hyperbolic functions (e.g. $x = \cosh(t)$, $y = \sinh(t)$).
\paragraph{Area} The area of a sector of the hyperbola is given by:
\begin{equation}
    A = t/2,
\end{equation} 
where $t$ is the angle of the sector along the parametrization $\{(x,y)\mid x = \cosh(t), y = \sinh(t)\}$.
\begin{figure}[h!]
    \begin{center}
        \begin{tikzpicture}[scale=0.8]
            % Draw the axes
            \draw[->] (-5, 0) -- (5, 0) node[right] {$x$};
            \draw[->] (0, -5) -- (0, 5) node[above] {$y$};

            % Draw ticks on the axes
            \foreach \x in {-4, -2, 2, 4}
                \draw (\x, 0.1) -- (\x, -0.1) node[below] {\x};
            \foreach \y in {-4, -2, 2, 4}
                \draw (0.1, \y) -- (-0.1, \y) node[left] {\y};

            % Draw the hyperbola branches
            \draw[thick, red, domain=-2:2, samples=100] plot ({cosh(\x)}, {sinh(\x)});
            \draw[thick, red, domain=-2:2, samples=100] plot ({-cosh(\x)}, {sinh(\x)});

            % Draw the asymptotes
            \draw[red, dashed] (-5, -5) -- (5, 5);
            \draw[red, dashed] (-5, 5) -- (5, -5);

            % Add a point on the hyperbola
            \coordinate (P) at ({cosh(1)}, {sinh(1)});
            \draw[fill] (P) circle (0.05) node[above right] {$(\cosh(t), \sinh(t))$};

            % Connect the labeled point to the origin
            \draw[thick, blue] (0, 0) -- (P);

            % Fill the sector area between hyperbola, line, and x-axis
            \fill[blue, opacity=0.3, domain=0:1, variable=\t]
                (0, 0) -- plot ({cosh(\t)}, {sinh(\t)}) -- cycle;
        \end{tikzpicture}
    \end{center}
    \caption{Sector of the hyperbola}
    \centering
\end{figure}
\paragraph{Catenary} The hyperbolic cosine function describes the shape of a hanging chain or cable. The catenary is the curve formed by a chain hanging from two points. It is given by the equation:
\begin{equation}
    a \cosh\left(\frac{x}{a}\right),
\end{equation}
\begin{definition}[Hyperbolic Tangent]
    The hyperbolic tangent function is defined as:
    \begin{equation}
        \tanh(x) = \frac{\sinh(x)}{\cosh(x)} = \frac{e^x - e^{-x}}{e^x + e^{-x}}. 
    \end{equation}
\end{definition}
\paragraph{Derivative} The derivative of the hyperbolic tangent function resembles the derivative of the regular tangent function:
\begin{equation} \frac{d}{dx} \tanh(x) = \text{sech}^2(x). \end{equation}
\paragraph{Identities} The hyperbolic tangent function satisfies the following identities:
\begin{align}
    \tanh(x) &= \frac{\sinh(x)}{\cosh(x)}, \\
    \text{sech}^2(x) &= 1 - \tanh^2(x).
\end{align}
\paragraph{Secant, Cosecant, Cotangent} The hyperbolic secant, cosecant, and cotangent functions are defined similarly to the regular secant, cosecant, and cotangent functions. They are the \textbf{reciprocal} of the hyperbolic cosine, sine, and tangent functions, respectively.
\paragraph{Inverse Hyperbolic Functions} The inverse hyperbolic functions are defined as the inverse of the hyperbolic functions. They are denoted by $\sinh^{-1}(x)$, $\cosh^{-1}(x)$, $\tanh^{-1}(x)$, etc.
\begin{align}
    \text{arsinh } x &= \ln\left(x + \sqrt{x^2 + 1}\right) \\[10pt]
    \text{arcosh } x &= \ln\left(x + \sqrt{x^2 - 1}\right) \\[10pt]
    \text{artanh } x &= \frac{1}{2} \ln\left(\frac{1 + x}{1 - x}\right) \\[10pt]
    \text{arcsch } x &= \ln\left(\frac{1}{x} + \sqrt{\frac{1}{x^2} + 1}\right) \\[10pt]
    \text{arsech } x &= \ln\left(\frac{1}{x} + \sqrt{\frac{1}{x^2} - 1}\right) \\[10pt]
    \text{arcoth } x &= \frac{1}{2} \ln\left(\frac{x + 1}{x - 1}\right)
\end{align}

\end{document}

### 2025-01-10 MAT185 Lecture Notes/main.tex
Add Force-Separation Curve and update lecture notes

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf MAT 185 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Linear Algebra, Winter 2024 \hfill MAT 185\\
\section{Vector Space}
\begin{definition}[Vector Space in $\mathbb{R}$]
    A vectors space,${V}$, over $\mathbb{R}$ is a collection of \textbf{object} $\textbf{v} \in V$ s.t. the follow axioms are followed
    \begin{enumerate}
        \item \textbf{Closure Under Addition} $\textbf{x},\textbf{y} \in V \implies \textbf{x} + \textbf{y} \in V$
        \item \textbf{Order of Addition} $\textbf{x},\textbf{y}, \textbf{z} \in V \implies (\textbf{x} + \textbf{y}) + \textbf{z} = \textbf{x} + (\textbf{y} + \textbf{z}) \in V$
        \item \textbf{Existence of Additional Identity} $\exists \textbf{0} \in V$ s.t. $\textbf{x} \in V \implies \textbf{x} + \textbf{0} = \textbf{x}$
        \item \textbf{Existence of Additional Inverse} $\forall \textbf{x} \in V \exists \textbf{-x} \in V$ s.t. $\textbf{x} + \textbf{-x} = \textbf{0}$
        \item \textbf{Closure under Scalar Multiplication} $\forall \textbf{x} \in V$ and $\forall \alpha \in \mathbb{R} \implies \alpha\textbf{x} \in V$
        \item \textbf{Order of Scalar Multiplication} $\forall \textbf{x} \in V$ and $\alpha, \beta \in \mathbb{R}$, $(\alpha\beta)\textbf{x} \implies \alpha(\beta\textbf{x})$
        \item \textbf{Distributive Scalar Multiplication} $\forall \textbf{x} \in V$ and $\alpha, \beta \in \mathbb{R}$, $(\alpha + \beta)\textbf{x} = \alpha\textbf{x} + \beta\textbf{x}$
        \item \textbf{Existence of Multiplicative Identity} $\forall \textbf{x} \in V$, $1\textbf{x} = \textbf{x}$
    \end{enumerate}
\paragraph{Note} It could be shown that the axiom imply the commutativity of in addition, namely $\forall \textbf{x} \implies \textbf{y} \in \mathbb{R}$, $\textbf{x} + \textbf{y} = \textbf{y} + \textbf{x}$
\end{definition}
\end{document}

>>>>

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf MAT 185 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Linear Algebra, Winter 2024 \hfill MAT 185\\
\section{Vector Space}
\begin{definition}[Vector Space in $\mathbb{R}$]
    A vectors space,${V}$, over $\mathbb{R}$ is a collection of \textbf{object} $\textbf{v} \in V$ s.t. the follow axioms are followed
    \begin{enumerate}
        \item \textbf{Addition Axioms}
        \begin{enumerate}
            \item \textbf{Closure Under Addition:} \\
            $\textbf{x}, \textbf{y} \in V \implies \textbf{x} + \textbf{y} \in V$

            \item \textbf{Associativity of Addition:} \\
            $\textbf{x}, \textbf{y}, \textbf{z} \in V \implies (\textbf{x} + \textbf{y}) + \textbf{z} = \textbf{x} + (\textbf{y} + \textbf{z})$

            \item \textbf{Existence of Additive Identity:} \\
            $\exists \, \textbf{0} \in V$ such that $\textbf{x} \in V \implies \textbf{x} + \textbf{0} = \textbf{x}$

            \item \textbf{Existence of Additive Inverse:} \\
            $\forall \, \textbf{x} \in V, \, \exists \, \textbf{-x} \in V$ such that $\textbf{x} + \textbf{-x} = \textbf{0}$
        \end{enumerate}

        \item \textbf{Scalar Multiplication Axioms}
        \begin{enumerate}
            \item \textbf{Closure Under Scalar Multiplication:} \\
            $\forall \, \textbf{x} \in V \, \text{and} \, \forall \, \alpha \in \mathbb{R}, \, \alpha \textbf{x} \in V$

            \item \textbf{Associativity of Scalar Multiplication:} \\
            $\forall \, \textbf{x} \in V \, \text{and} \, \forall \, \alpha, \beta \in \mathbb{R}, \, (\alpha \beta) \textbf{x} = \alpha (\beta \textbf{x})$

            \item \textbf{Distributive Property of Scalar Multiplication:} \\
            $\forall \, \textbf{x} \in V \, \text{and} \, \forall \, \alpha, \beta \in \mathbb{R}, \, (\alpha + \beta) \textbf{x} = \alpha \textbf{x} + \beta \textbf{x}$

            \item \textbf{Existence of Multiplicative Identity:} \\
            $\forall \, \textbf{x} \in V, \, 1 \textbf{x} = \textbf{x}$
        \end{enumerate}
    \end{enumerate}

    \paragraph{Note} It could be shown that the axiom imply the commutativity of in addition, namely $\forall \textbf{x} \implies \textbf{y} \in \mathbb{R}$, $\textbf{x} + \textbf{y} = \textbf{y} + \textbf{x}$
\end{definition}
\paragraph{Example} $\mathbb{R}^n$ is a vector space over $\mathbb{R}$, where $\textbf{x} = (x_1, x_2, \ldots, x_n)$ and $\textbf{y} = (y_1, y_2, \ldots, y_n)$, then $\textbf{x} + \textbf{y} = (x_1 + y_1, x_2 + y_2, \ldots, x_n + y_n)$ and $\alpha\textbf{x} = (\alpha x_1, \alpha x_2, \ldots, \alpha x_n)$
\begin{theorem}[Cancelation, Part 1]
    Let $V$ be a vector space and $\textbf{x}, \textbf{y}, \textbf{z} \in V$, then:
    \begin{align*}
        \textbf{x} + \textbf{z} &= \textbf{y} + \textbf{z} \\
        \textbf{x} &= \textbf{y}
    \end{align*} 
\end{theorem}
\begin{proof}
    \begin{align*}
        \textbf{x} + \textbf{z} &= \textbf{y} + \textbf{z} \\
        \intertext{From additive inverse we know that \textbf{-z} exists}
        (\textbf{x} + \textbf{z}) + \textbf{-z} &= (\textbf{y} + \textbf{z}) + \textbf{-z} \\
        \intertext{By order of addition we have: }
        \textbf{x} + (\textbf{z} + \textbf{-z}) &= \textbf{y} + (\textbf{z} + \textbf{-z}) \\
        \textbf{x} + \textbf{0} &= \textbf{y} + \textbf{0} \\
        \intertext{By additive identity we have: }
        \textbf{x} &= \textbf{y}
    \end{align*}
\end{proof}
\begin{theorem}[Cancelation, Part 2]
    Let $V$ be a vector space and $\textbf{x}, \textbf{y}, \textbf{z} \in V$, then:
    \begin{align*}
        \textbf{z} + \textbf{x} &= \textbf{z} + \textbf{y} \\
        \textbf{x} &= \textbf{y}
    \end{align*} 
\end{theorem}
To proof that, it would require the following propostion:
\begin{lemma}
    Let $V$ be a vector space and $\textbf{z} \in V$, then $\textbf{-z} + \textbf{z} = 0 $
\end{lemma}
\begin{proof}
    \begin{align*}
        \intertext{We know:}
        \textbf{-z} + \textbf{z} &= (\textbf{-z} + \textbf{z}) + 0\\
        &= (\textbf{-z} + \textbf{z}) + (\textbf{-z} + \textbf{-(-z)}) \\
        \intertext{By the order of additon, }
        &= \textbf{-z} + (\textbf{z} + (\textbf{-z} + \textbf{-(-z)})) \\
        \intertext{Again, by the order of additon, }
        &= \textbf{-z} + ((\textbf{z} + \textbf{-z}) + \textbf{-(-z)}) \\
        &= \textbf{-z} + \textbf{-(-z)} \\
        &= 0
    \end{align*}
\end{proof}
Now, to prove the part 2 of the Cancelation Theorem:
\begin{proof}
    \begin{align*}
        \textbf{z} + \textbf{x} &= \textbf{z} + \textbf{y} \\
        \intertext{From additive inverse we know that \textbf{-z} exists}
        \textbf{-z} + (\textbf{z} + \textbf{x}) &= \textbf{-z} + (\textbf{z} + \textbf{y})\\
        (\textbf{-z} + \textbf{z}) + \textbf{x} &= (\textbf{-z} + \textbf{z}) + \textbf{y}\\
        \intertext{From above, we have $\textbf{-z} + \textbf{z} = 0$}
        0 + \textbf{x} &= 0 + \textbf{y} \\
        \textbf{x} &= \textbf{y}
    \end{align*}
\end{proof}
\begin{lemma}[Inverse of an inverse]
    Let $V$ be a vector space and $\textbf{x} \in V$, then:
    \begin{align*}
        \textbf{-(-x)} &= \textbf{x}
    \end{align*}
\end{lemma}
\begin{proof}
    Assume $0$, $0^\star$ are the additive identity of $V$ and $\textbf{-x}$, $\textbf{-x}^\star$ are the additive inverse of $\textbf{x}$. We have:
    \begin{equation*}
        u+0 = u + 0^\star
    \end{equation*}
    By Cancelation Theorem, we have $0 = 0^\star$. Thus, the additive identity is unique. Now, we have:
    \begin{align*}
        \textbf{x} + \textbf{-x} &= 0 \\
        \textbf{x} + \textbf{-x}^\star &= 0
        \intertext{Thus, by the uniqueness of the additive inverse, we have:}
        \textbf{x} + \textbf{-x} &= \textbf{x} + \textbf{-x}^\star
        \intertext{By the Cancelation Theorem, we have:}
        \textbf{-x} &= \textbf{-x}^\star
    \end{align*}
    Now, we have that the additive inverse is unique. Thus, $\textbf{-(-x)}$ must be unique and nessarily $\textbf{x}$. 
\end{proof}
\paragraph{Results from above}
\begin{enumerate}
    \item The additive identity is unique
    \item The additive inverse is unique
\end{enumerate}
\begin{definition}[Subtraction]
    Let $V$ be a vector space and $\textbf{x}, \textbf{y} \in V$, then:
    \begin{align*}
        \textbf{x} - \textbf{y} &\defeq \textbf{x} + \textbf{-y}
    \end{align*}
\end{definition}
\begin{theorem}[Commutativity of Addition]
    Let $V$ be a vector space and $\textbf{x}, \textbf{y} \in V$, then:
    \begin{align*}
        \textbf{x} + \textbf{y} &= \textbf{y} + \textbf{x}
    \end{align*} 
\end{theorem}
\begin{proof}
    \begin{align*}
        \textbf{x} + \textbf{y} &=  
    \end{align*}
\end{proof}   
\end{document}
